A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-01 example.tex
Image descriptions

\begin{figure}[ht]
    \centering 
  \begin{subfigure}[b]{\autscale\textwidth}
    \centering
    \includegraphics[width=\textwidth]{a}
    \caption{The automaton $A'$, whose Parikh registers count the length of the
    string accepted by the automaton (register $l_A$), the start offset of the
    substring ($i$) and length ($n$) of the substring matching
    $\Regex{c\RegexOr{}dd}$. Note the symbolic transitions in the starting and
    accepting states matching any symbol in the alphabet!}\label{fig:aut_a}
      %\Description[SHORT]{LONG}
  \end{subfigure}%
  \hfill%
  \begin{subfigure}[b]{\autscale\textwidth}
    \centering
    \includegraphics[width=\textwidth]{b}
    \caption{The automaton $B$, where the Parikh registers count the length of
    the string in register $l_B$.}\label{fig:aut_b}
      %\Description[SHORT]{LONG}
  \end{subfigure}
  \caption{The collection of automata we use as running
  examples, both derived from \cref{ex:string-constraints}.}\label{fig:examples}
\end{figure}

@@

\begin{figure}[tb]
  \centering 
  \includegraphics[width=0.6\textwidth]{a_2}
  \caption{ $\mathcal{A}'$ after even more simplification using linear algebra,
   with most transitions expressed
  in terms of $n$. Intuitively, this version captures the fact that $n$ is given
  by distributing the incoming flow of $1$ across the two outgoing transitions
  from $I_{A'}$, the initial state.}
  \label{fig:a_2}
\end{figure}

\begin{figure}[ht]
  \centering 
\begin{subfigure}{0.42\textwidth}
  \centering
  \includegraphics[width=\textwidth]{a_annotated}
  \vspace*{5ex}
  \caption{ $\mathcal{A}'$ with its associated transition variables in symbolic
  form.}\label{fig:aut_a_annotated}
    %\Description[SHORT]{LONG}
  \vspace*{1.9ex}
\end{subfigure}\hfill%
\begin{subfigure}{0.54\textwidth}
  \centering
  \includegraphics[width=\textwidth]{b_annotated}
  \caption{$\mathcal{B}$ with its associated transition variables in symbolic forms.
  The large number of implicitly existentially quantified
  variables~$x_i$ on
  transitions suggest that this automaton has a more complex structure
  with relation to its (free) target variable representing the string length
  than $\mathcal{A}'$. %The variables used here are fresh, and do not correspond to the
  % ones previously used.
}\label{fig:aut_b_annotated}
    %\Description[SHORT]{LONG}
\end{subfigure}
\caption{The automata after arithmetic simplification.}\label{fig:propagated}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering 
  \begin{subfigure}[b]{\autscale\textwidth}
    \centering
    \includegraphics[width=\textwidth]{a}
    \caption{The automaton $A'$, whose Parikh registers count the length of the
    string accepted by the automaton (register $l_A$), the start offset of the
    substring ($i$) and length ($n$) of the substring matching
    $\Regex{c\RegexOr{}dd}$. Note the symbolic transitions in the starting and
    accepting states matching any symbol in the alphabet!}\label{fig:aut_a}
      \Description[A 3-state Parikh automaton.]{%
      A 3-state Parikh automaton with two registers counting the length
      of a substring matching c or dd.%
      }
  \end{subfigure}%
  \hfill%
  \begin{subfigure}[b]{\autscale\textwidth}
    \centering
    \includegraphics[width=\textwidth]{b}
    \caption{The automaton $B$, where the Parikh registers count the length of
    the string in register $l_B$.}\label{fig:aut_b}
      \Description[A 4-state Parikh automaton.]{%
      A 4-state Parikh automaton with initial state IB going to the B state,
      which counts a number of letters c, followed by one final c before reaching 
      the accepting state, FB. The second path from the initial state consumes an a,
      goes into state A, consumes some number of c:s, followed by a final a to get to
      the accepting state.}
  \end{subfigure}
  \caption{The collection of automata we use as running
  examples, both derived from \cref{ex:string-constraints}.}\label{fig:examples}
\end{figure}

@@

\begin{figure}[tb]
  \centering 
  \includegraphics[width=0.6\textwidth]{a_2}
  \caption{ $\mathcal{A}'$ after even more simplification using linear algebra,
   with most transitions expressed
  in terms of $n$. Intuitively, this version captures the fact that $n$ is given
  by distributing the incoming flow of $1$ across the two outgoing transitions
  from $I_{A'}$, the initial state.}
  \Description[A 3-state automaton, with equations on its labels.]{%
  The initial state accepts any character and is labelled with the variable i. From
  that state there is a transition to the D state reading d with $n-1$ and one reading c
  going directly to the final state. The second transition is labelled with the equation
  $2-n$. The final state has one transition that consumes any character with the equation 
  $l_A-i-n$.%
  }
  \label{fig:a_2}
\end{figure}

\begin{figure}[ht]
  \centering 
\begin{subfigure}{0.42\textwidth}
  \centering
  \includegraphics[width=\textwidth]{a_annotated}
  \vspace*{5ex}
  \caption{ $\mathcal{A}'$ with its associated transition variables in symbolic
  form.}\label{fig:aut_a_annotated}
    %\Description[A 3-state automaton with ]{LONG}
  \vspace*{1.9ex}
\end{subfigure}\hfill%
\begin{subfigure}{0.54\textwidth}
  \centering
  \includegraphics[width=\textwidth]{b_annotated}
  \caption{$\mathcal{B}$ with its associated transition variables in symbolic forms.
  The large number of implicitly existentially quantified
  variables~$x_i$ on
  transitions suggest that this automaton has a more complex structure
  with relation to its (free) target variable representing the string length
  than $\mathcal{A}'$. %The variables used here are fresh, and do not correspond to the
  % ones previously used.
}\label{fig:aut_b_annotated}
    %\Description[SHORT]{LONG}
\end{subfigure}
\caption{The automata after arithmetic simplification.}\label{fig:propagated}
\end{figure}
